### 2015-01-10 paper/Content/sources.tex
Added Fowler; added MVP UML-like graphic

>>>>

\bibitem{FowlerMvpRetirementNote}
Fowler, Martin: \emph{Retirement note for Model View Presenter Pattern},
[Online]. http://martinfowler.com/eaaDev/ModelViewPresenter.html (retrieved 10-Jan-2015)

\bibitem{FowlerSupervisingController}
Fowler, Martin: \emph{Supervising Controller},
[Online]. http://martinfowler.com/eaaDev/SupervisingPresenter.html (retrieved 10-Jan-2015)

\bibitem{FowlerPassiveView}
Fowler, Martin: \emph{Passive View},
[Online]. http://martinfowler.com/eaaDev/PassiveScreen.html (retrieved 10-Jan-2015)
